Double White Dwarf Mergers on Adaptive Meshes\\ I. Methodology and Code Verification

### 2015-07-19 papers/wdmerger_I/paper.tex
Switch to solely using the journal commands provided by the emulateapj class, so that we are fully consistent.
Add a note on refluxing to the paper.

%\documentclass[12pt,preprint]{../aastex}
\documentclass[iop]{../emulateapj}
% for \sout
\usepackage{ulem}
% makes sure \em{} is italic rather than underlined (corrects ulem from line above)
\normalem

@@

>>>>

\documentclass[iop]{../emulateapj}
% for \sout
\usepackage{ulem}
% makes sure \em{} is italic rather than underlined (corrects ulem from line above)
\normalem

@@

A final issue worth noting relates to complications posed by mesh refinement. Like 
many AMR codes, CASTRO implements a refluxing algorithm at the end of a timestep. 
At any locations on a particular grid level that are adjacent to, but not covered by,
zones from a finer grid, there will be a disagreement about the fluxes crossing 
this coarse-fine interface. If left uncorrected, this results in a violation of 
the conservation condition. Therefore the value of the coarse flux on this interface 
is replaced by the sum of the fine fluxes at that interface, at the end of the 
coarse timestep. In general, this change in mass distribution on the grid 
results in a change in the gravitational potential, meaning that an additional 
corrective source term ought to be added. \cite{miniati:2007} and \cite{castro} 
describe an algorithm for doing so. We consider the size of this effect to be 
negligible and therefore we avoid the expense of solving for the potential change caused by 
this mass change. Our grid boundaries are always located outside of the dense 
stellar interiors that generate almost all of the gravitational potential. 
Consequently the refluxing operation only changes the solution in regions of 
ambient density, and even there only to the extent that there is disagreement 
between the coarse and fine fluxes -- this clearly has a 
vanishingly small effect on the gravitational potential.
